\documentclass{article}
\begin{document}
\textbf{Sprint 2 - 10.02.25–22.02.25} 
\textbf{Sprint Goal} 

\section{Goals for the sprint:}

\subsection{Front-End:}
\begin{itemize}
    \item Create basic HTML for all Wireframe pages of the application.
    \begin{itemize}
        \item Header
        \item Footer
        \item Front page
        \item Car selection page
        \item Menu when selecting a car
        \item Login/Register popup/page
        \item Page for filling out form 
    \end{itemize}
    \item Design logo
\end{itemize}

\subsection{Back-End:}
\begin{itemize}
    \item Create Entity-Relationship Diagram (ERD) for the database
    \item Start building basic structure for REST API
\end{itemize}

\subsection{Questions for next meetup:}

\subsubsection{Use case diagram:}
\begin{itemize}
    \item Should admin be able to do absolutely everything? Can we make a single arrow for him (admin mode) so we don't have to draw an arrow to every action?
    \item How should we implement special features for admin? Obviously an admin does not need a pretty GUI - is a custom terminal enough?
    \item Should car rental providers be able to rent cars?
    \item Should we allow for businesses to rent cars?
\end{itemize}

\subsubsection{Database:}
Do we need a separate table where we list all privileges and connect them to account.id? OR

Is it best if we implement a check for roles before processing a rental like this:

DELIMITER //
CREATE TRIGGER block-admin-rentals
BEFORE INSERT ON rentals
FOR EACH ROW
BEGIN
    IF (SELECT role FROM accounts WHERE id = NEW.renter-id) = 'ADMIN' THEN
        SIGNAL SQLSTATE '45000' SET MESSAGE\_TEXT = 'Admins can’t rent.';
    END IF;
END//
DELIMITER ;


\section{\textbf{Use case structure:}}

\subsection{Admin:}
\begin{itemize}
    \item 
\end{itemize}

\subsection{Unregistered User}

\subsection{Registered User}

\subsection{Car rental provider}



\end{document}