% Setting up the document with a comprehensive preamble
\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\setlength{\parindent}{0pt}
\title{Sprint 6 Plan}
\author{Team}
\date{May 20, 2025}

\begin{document}

\maketitle

\section*{Sprint 6 - 10.05.25--24.05.25}
\textbf{Sprint Goal}

\begin{itemize}
    \item Finalize the Aalesund Rental app for production release
    \begin{itemize}
        \item Enhance user interface consistency and usability
        \begin{itemize}
            \item Standardize font sizes and create visual hierarchies using boldness and brightness
            \item Display saved filter changes upon closing and opening of filter menus
        \end{itemize}
        \item Fix critical bugs
        \begin{itemize}
            \item Fix homepage issues
            \item Fix car type filtering on rental page
            \item Fix CSS formatting issue on booking page 
            \item Fix search cars button in header to trigger reload with new parameters
            \item Fix location drop-down menu to appear in header on rental page
            \item Fix issue where user cannot access /account right after logging in
            \item Fix "Book now" section call at the bottom of the booking-page
            \item Make cancel order button disappear when order is cancelled
            \item Add search filter and price filter to mobile display size on rental page
        \end{itemize}
        \item Improve functionality and user experience
        \begin{itemize}
            \item Show "No cars found" when no cars are found on rental page
            \item Make featured cars section display cars from rental page
            \item Make pickup location a required field to view rentals
            \item Finish "My Rentals" page
            \item Create a favorites page
            \item Create a wiki-page
        \end{itemize}
        \item Finalize back-end and database
        \begin{itemize}
            \item Add search bar for rentals page
            \item Make "Book now" button complete a booking with a POST request
            \item Add constraints to database
            \item Add detailed logging
            \item Store database passwords and JWT secret key in environment files
            \item Add refresh-token to the database
            \item Implement token-refresh endpoint for the backend
            \item Fix expiration date on tokens
            \item Finish token-refresh functionality
            \item Make a check on backend for disabled accounts
            \item Add a pop-up confirmation page for 'Cancel Order' in 'account/orders'
            \item Set up connection between REST-APIs and the container
            \item Use 'useLoaderData' from react-router-dom to load data from database to front-end
            \item Secure backend and frontend with HTTPS
            \item Provide re-entrant test set
            \item Document API endpoints
        \end{itemize}
        \item Finalize project requirements
        \begin{itemize}
            \item        Include README file(s) in the project
            \item Look over code quality and accessibility
            \item Look over deliverables
            \item Create video presentation
            \item Prepare demo data
        \end{itemize}

    \end{itemize}
\end{itemize}

\section*{Sprint Backlog}

\textbf{Time Frame}

10.05.25--24.05.25

\textbf{Roles and Responsibilities}

\begin{itemize}
    \item \textbf{Marcus (MSkaue)} $\rightarrow$ All, responsible specifically for Documentation and Front-End
    \item \textbf{Mathias (mathiaslovnes)} $\rightarrow$ All, responsible specifically for Front-End and Back-End
    \item \textbf{Petter (PetterJY)} $\rightarrow$ All, responsible specifically for Back-End  and Database
\end{itemize}

\section*{Expected Results}

\begin{enumerate}
    \item \textbf{Enhanced User Interface Consistency and Usability}
    \begin{itemize}
        \item Standardized font sizes and visual hierarchies using boldness and brightness for a cohesive look.
        \item Filter menus display saved changes and show the number of selected filters.
    \end{itemize}
    \item \textbf{Resolved Critical Bugs}
    \begin{itemize}
        \item Homepage issues resolved for a polished user experience.
        \item Car type filtering fully functional on the rental page.
        \item CSS formatting issue on booking page fixed.
        \item Search cars button in header triggers reload with new parameters.
        \item Location drop-down menu appears in header on rental page.
        \item Users can access /account immediately after logging in.
        \item "Book now" section call at page bottom fixed.
        \item Cancel order button disappears when an order is cancelled.
        \item Search and price filters functional on mobile display sizes.
    \end{itemize}
    \item \textbf{Improved Functionality and User Experience}
    \begin{itemize}
        \item "No cars found" message displayed when no cars match filters on rental page.
        \item Featured cars section displays cars from the rental page.
        \item Pickup location set as a required field to view rentals.
        \item "My Rentals" page fully functional, showing user rental details.
        \item Favorites page created, allowing users to manage favorite cars.
        \item Wiki-page created to document app usage and features.
    \end{itemize}
    \item \textbf{Finalized Back-End and Database}
    \begin{itemize}
        \item Service and Repository classes implemented for modular back-end logic.
        \item Controller and database table for favorites fully functional.
        \item Search bar added to rentals page, integrated with back-end.
        \item "Book now" button sends POST request to complete bookings.
        \item Database constraints added to ensure data integrity.
        \item Detailed logging implemented for debugging and monitoring.
        \item Database passwords and JWT secret key stored securely in environment files.
        \item Refresh-token stored in the database and token-refresh endpoint implemented.
        \item Token expiration dates fixed and token-refresh functionality completed.
        \item Backend check for disabled accounts implemented.
        \item Pop-up confirmation page added for 'Cancel Order' in 'account/orders'.
        \item REST-APIs connected to the container for seamless operation.
        \item 'useLoaderData' used to load database data to the front-end efficiently.
    \end{itemize}
\item \textbf{Finalized project requirements}
    \begin{itemize}
        \item Include the README file(s) in the project
        \item The code quality and accessibility is as expected
        \item All the deliverables are ready to get handed in.
        \item Have a video presentation lasting between 12-15 min
        \item Have a demo data to demonstrate different scenarios.
    \end{itemize}
\end{enumerate}

\end{document}