\documentclass{article}
\begin{document}
\textbf{Sprint 3 - 04.03.25–28.03.25} 
\textbf{Sprint Retrospective} 

\textbf{Note:}
We originally planned for the sprint to last for 2 weeks, and not 3. However, due to large group assignments in both App-dev and operating systems courses, we decided to extend it for an additional week.

\subsection{Intended goals:}
\begin{itemize}
    \item Make most pages of the site more responsive and flexible to smaller screen sizes:
    \item Create the entity-, logic-, and repository-classes for the backend using JPA.
    \item Create wireframes for smaller screen sizes.
    \item Create account page.
\end{itemize}

\subsection{Completed goals}
\begin{itemize}
    \item Created the database structure in Java using JPA.
    \item Created wireframes for mobile versions of: Rental page, home page and booking page.
\end{itemize}

\subsection{Incomplete Goals}
\begin{itemize}
    \item Wireframes for medium-sized screen sizes (tablets).
    \item Write the code for the envisioned selected-car page (appears when clicking a car to view its details).
\end{itemize}
   
\subsection{Things we should maintain:}
\begin{itemize}
    \item Clear API documentation with Swagger.
    \item Effective and structured use of version control - consistent commits with detailed commit messages, as well as use of branches for experimental feature development.
    \item Team communication - effective division of tasks, everybody knew what others were working on, no merge conflicts occurred.
\end{itemize}

\subsection{Things we could do differently:}
\begin{itemize}
\item  Taking a look at all issues on the issue board and prioritize them according to their value in achieving an MVP, avoiding neglecting old issues.
    \item Order group rooms a week ahead of time so that we'd waste less time wandering around trying to find a place to work.
\end{itemize}

\end{document}