% Setting up the document with a comprehensive preamble
\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\setlength{\parindent}{0pt}
\title{Sprint Retrospective}
\author{Team}
\date{April 20, 2025}

\begin{document}

\maketitle
\textbf{Sprint 4 - 30.03.25–20.04.25} 

\section*{Sprint Overview}
This sprint focused on advancing back-end functionality and API development for our rental platform. We successfully completed all planned goals. Each member of the team contributed to all tasks, demonstrating strong collaboration and shared responsibility.

\section*{Sprint Goals}
\begin{itemize}
    \item Differentiate between account types in the back-end.
    \item Enable user account creation in the back-end.
    \item Connect a rental order to its provider, car, and user (renter).
    \item Implement CRUD REST API functionality.
    \item Add Swagger documentation to all new code.
    \item Make front-end more responsive.
\end{itemize}

\section*{What Went Well}
\begin{itemize}
    \item \textbf{Team Collaboration}: We worked well together, with each member contributing to all goals. This shared responsibility ensured a balanced workload and encouraged knowledge sharing.
    \item \textbf{Goal Completion}: All sprint goals were met on time, including complex tasks such as connecting rental orders and implementing CRUD REST API functionality.
    \item \textbf{Documentation Quality}: The team successfully integrated Swagger documentation for all new code, improving maintainability and clarity for future development.
    \item \textbf{Efficient Task Allocation}: The overlap of responsibilities allowed for flexibility, enabling the team to quickly address blockers and maintain momentum.
    \item \textbf{Peer Programming}: Continue with the peer programming so that everyone learns everything
\end{itemize}

\section*{What Could Be Improved}
\begin{itemize}
    \item \textbf{Testing Coverage}: Although all goals were completed, an additional focus on automated testing could ensure greater robustness, especially for the CRUD API and account differentiation logic.
    \item \textbf{Time Estimation}: Some tasks, such as connecting rental orders, took longer than anticipated due to unforeseen complexities. Improved estimation techniques could help in future sprints.
\end{itemize}

\section*{Action Items for Next Sprint}
\begin{itemize}

    \item \textbf{Enhance Testing}: Incorporate unit and integration tests for all new back-end features to ensure reliability and reduce bugs.
    \item \textbf{Refine Estimation}: Retrospective insights are used to improve time estimates, potentially breaking down complex tasks into smaller and more predictable units.
\end{itemize}

\section*{Team Acknowledgment}
The team’s dedication and collaborative spirit of the team were the key to the success of this sprint. We demonstrated strong teamwork, ensuring that all goals were met. 

\end{document}