% Setting up the document with a comprehensive preamble
\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\setlength{\parindent}{0pt}
\title{Sprint 5 Plan}
\author{Team}
\date{May 20, 2025}

\begin{document}

\maketitle

\section*{Sprint 5 - 21.04.25--09.05.25}
\textbf{Sprint Goal}

\begin{itemize}
    \item Enhance user interface and functionality for the Aalesund Rental platform
    \begin{itemize}
        \item Implement filtering and navigation features
        \begin{itemize}
            \item Add price range filter with visual slider
            \item Add filtering feature for cars
            \item Add save changes button next to filters for non-phone-sized screens
        \end{itemize}
        \item Improve provider account functionality
        \begin{itemize}
            \item Style drop-down menu for account
            \item Create "Add Car" button/menu for providers
            \item Create "My Cars" page for providers in account
            \item Create "Orders" page for users to see their car orders.
            \item Add image mapping to relevant cars.
        \end{itemize}
        \item Enhance user experience
        \begin{itemize}
            \item Create "Site not found" page
            \item Update header on login
        \end{itemize}
        \item Initialize database content
        \begin{itemize}
            \item Create template objects for cars, rentals, users, etc. in the database
        \end{itemize}
    \end{itemize}
\end{itemize}

\section*{Sprint Backlog}

\textbf{Time Frame}

21.04.25--09.04.25

\textbf{Roles and Responsibilities}

\begin{itemize}
    \item \textbf{Marcus (MSkaue)} $\rightarrow$ Improve provider account functionality, Initialize database content.
    \item \textbf{Mathias (mathiaslovnes)} $\rightarrow$ Implement filtering and navigation features
    \item \textbf{Petter (PetterJY)} $\rightarrow$ Improve provider account functionality, Enhance user experience. 
\end{itemize}

\section*{Expected Results}

\begin{enumerate}
    \item \textbf{Enhanced Filtering Features}
    \begin{itemize}
        \item Price range filter with a visual slider implemented and functional.
        \item Car filtering feature available, allowing users to filter cars based on criteria.
        \item Save changes button implemented for non-phone-sized screens.
    \end{itemize}
    \item \textbf{Improved Provider Account Functionality}
    \begin{itemize}
        \item Styled drop-down menu for account, improving usability and aesthetics.
        \item "Add Car" button/menu implemented, enabling providers to add cars easily.
        \item "My Cars" page created, allowing providers to view and manage their cars.
        \item "Orders" page created, allowing users to view their rental orders.
        \item Image mapping give users and providers a visual representation of the cars.
    \end{itemize}
    \item \textbf{Enhanced User Experience}
    \begin{itemize}
        \item "Site not found" page created to handle invalid URLs gracefully.
        \item  Update header based on the user that i logged in. 
    \end{itemize}
    \item \textbf{Database Initialization}
    \begin{itemize}
        \item Template objects for cars, rentals, users, etc., added to the database to support development and testing.
    \end{itemize}
\end{enumerate}


\end{document}